Ripple Protocol Consensus Algorithm Review

### 2015-05-11 paper.tex
close to finished

The Ripple consensus review investigation had four major activities associated
with it:

@@

    \item The main implementation of the Ripple protocol, \texttt{rippled}, does
        not cleanly separate the consensus-critical part of the codebase from
        the non-consensus-critical part.\footnote{The consensus-critical
            portions of Bitcoin Core codebase are currently being separated
            into a stand-alone \emph{libconsensus} library.}

>>>>

Four major activities were performed during the review:

@@

    \item The main implementation of the Ripple protocol, \texttt{rippled}, does
        not cleanly separate the consensus-critical part of the codebase from
        the non-consensus-critical part.\footnote{The consensus-critical
            portions of Bitcoin Core codebase are currently being separated
            into a stand-alone \texttt{libconsensus} library.}
